Analysis

### 2023-12-11 Analysis.rmd
Respond to review comments

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)
library(dplyr)
library(tidyr)
library(forcats)
library(scales)

colors <- RColorBrewer::brewer.pal(n = 9, name = "Set1")
colors <- hex <- hue_pal()(4)

@@

@@

@@

# Figure 1: Number of forecasters across the study period
================================================================================
- numbers of forecasters used in the text

@@

# Figure 2: Predictive performance across horizons (summary)
================================================================================

@@

# Figure 3: Forecasts and corresponding WIS
================================================================================

@@

# Figure 4: Ranks for different models
================================================================================

@@

# Figure 5: Comparison performance direct vs. Rt
================================================================================

@@

# Figure 6: Performance of "experts" and "non-experts"
================================================================================
Separate ensemble of experts and non-experts

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
# use scoringutils version 1.2.2: remotes::install_github("epiforecasts/scoringutils@v1.2.2")
library(scoringutils) 
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)
library(dplyr)
library(tidyr)
library(forcats)
library(scales)

colors <- RColorBrewer::brewer.pal(n = 9, name = "Set1")
colors <- hex <- scales::hue_pal()(4)

@@

authors <- c("seb", "seabbs", "nib", "anonymous_Human")
models_authors <- c(authors, paste(authors, "(Rt)"))

@@

# Figure 1: overview of the data

```{r}
plot_data_simple <- function(weekly_truth, daily_truth) {
  weekly_truth |>
    mutate(status = str_to_title(status)) |>
  ggplot(aes(x = target_end_date, y = true_value)) +
  annotate("rect", xmin = time_start, xmax = time_stop, ymin = -Inf, ymax = Inf,
           fill = "darkolivegreen3", alpha = .1) + 
  geom_line() + 
  geom_point(size = 0.8) + 
  geom_bar(data = daily_truth |>
             mutate(true_value = true_value * 7), 
           stat = "identity", 
           fill = "skyblue3", alpha = 0.4) + 
  facet_wrap(~ target_type, 
             nrow = 2, scale = "free_y") + 
  scale_y_continuous(labels = label_fn) +
  theme_scoringutils() +
  labs(y = "Observed values", x = "Date", color = "Data status")
}

p_data <- plot_data_simple(weekly_truth, daily_truth)
ggsave("output/figures/overview-data.png", plot = p_data, 
       width = 7, height = 5)

weekly_truth |>
  filter(target_end_date >= time_start & target_end_date <= time_stop) |>
  filter(target_type == "Cases") |>
  pull(target_end_date)

Author participation

all <- forecasts |> 
  filter(!is.na(prediction), 
         model %in% models_human,
         horizon == 2) |>
  avail_forecasts(by = c("model", "target_type"))

authors <- forecasts |> 
  filter(!is.na(prediction), 
         model %in% models_authors,
         horizon == 2) |>
  avail_forecasts(by = c("model", "target_type"))

num_all <- all$`Number forecasts` |> sum()
num_authors <- authors$`Number forecasts` |> sum()

num_authors / num_all

@@

# Figure 2: Number of forecasters across the study period
================================================================================
- numbers of forecasters used in the text

@@

# Figure 3: Predictive performance across horizons (summary)
================================================================================

@@

# Figure 4: Forecasts and corresponding WIS
================================================================================

@@

# Figure 5: Ranks for different models
================================================================================

@@

# Figure 6: Comparison performance direct vs. Rt
================================================================================

@@

# Figure 7: Performance of "experts" and "non-experts"
================================================================================
Separate ensemble of experts and non-experts
